\hypertarget{namespace_hannes_o_o_p_project}{}\section{Hannes\+O\+O\+P\+Project Namespace Reference}
\label{namespace_hannes_o_o_p_project}\index{Hannes\+O\+O\+P\+Project@{Hannes\+O\+O\+P\+Project}}


This project aims to simulate the binding of immune cells to artificial beads decorated with molecules that induce a biological response of the cells.  




\subsection{Detailed Description}
This project aims to simulate the binding of immune cells to artificial beads decorated with molecules that induce a biological response of the cells. 

In nature, immene cells express receptors (so-\/called lectins) binding to carbohydrate structures, or glycans, on the surface of body\textquotesingle{}s own cells or pathogens. Depending on the nature of the glycan ligand, cells express specific cytokines, e. g. the pro-\/inflammatory I\+L-\/6. The idea of the biochemical is to investigate the biological response of a monocytic cell line which recombinantly expresses a defined set of lectin receptors upon binding to glycan ligands that are chemically linked to acrylic glass beads in well-\/defined amounts.

In the following, the translation of real-\/world dimensions for this project will be explained.

Monocytes are 5--20 um in diameter, while beads typically are few um in size. By definition, 1 pt in this program corresponds to 10 um in reality. The (round) basis of a well used in these experiments has an area of 0.\+36 qcm. Here, we consider a quadratic basis, hence $x=y=0.06 cm=600 pt$. Typical volume is 25 ul. Hence, the height of the liquid in a well is \[ h = \frac{25 \mu l}{b} = \frac{25 \cdot 10^{-8} m^3}{0.36 cm^2} = 41.67 \cdot 10^{-4} m = 420 pt. \] The number of cells usually used in these experiments is 50,000, incubated with a five-\/fold excess of beads. To make calculations feasible, the well dimension are reduced ten-\/fold in every dimension. In order to maintain equal density of particles, the number of cells and beads are consequently reduced to 50 and 250, respectively.

The incubation time of the cells with beads amounts to 30 minutes, or 1800 s. In order to determine to many steps that correlates to, the Stokes-\/\+Einstein equation was utilized\+: \[ x^2 = \frac{k_B \cdot T}{6r \pi \eta} t = \frac{1.381 \cdot 10^{-23} J/K \cdot 298 K}{6 \cdot 5 \mu m \cdot \pi \cdot 0.891 mPa \cdot s} = 9.8 \cdot 10^{-13} \frac{m^2}{s} \cdot t \] At 1 s, a particle of 10 um in aqueous solution would diffuse (ignoring the influence of gravity on sinking particles)\+: \[ \sqrt{x^2} = \sqrt{4.9 \cdot 10^{-13} \frac{m^2}{s} \cdot 1s} = 7 \cdot 10^{-7} m.\] Therefore, a typical experiment of 30 minutes corresponds to $ 1800 s \cdot 0.7 \mu m/s = 1260 \mu m = 126\mbox{ steps}. $

In summary, the values used are\+: \tabulinesep=1mm
\begin{longtabu} spread 0pt [c]{*{4}{|X[-1]}|}
\hline
\rowcolor{\tableheadbgcolor}\textbf{ Parameter  }&\textbf{ Value ({\itshape in vitro})  }&\textbf{ Value ({\itshape in silico})  }&\textbf{ Reduced value   }\\\cline{1-4}
\endfirsthead
\hline
\endfoot
\hline
\rowcolor{\tableheadbgcolor}\textbf{ Parameter  }&\textbf{ Value ({\itshape in vitro})  }&\textbf{ Value ({\itshape in silico})  }&\textbf{ Reduced value   }\\\cline{1-4}
\endhead
Cell size  &5-\/20 um  &1 pt  &---   \\\cline{1-4}
Bead size  &few um  &1 pt  &---   \\\cline{1-4}
Well basis  &0.\+36 qcm  &600 pt $\ast$ 600 pt  &60 pt, 60 pt   \\\cline{1-4}
Volume  &25 ul  &basis $\ast$ 420 pt  &42 pt   \\\cline{1-4}
Number of cells  &50,000  &50,000  &50   \\\cline{1-4}
Number of beads  &250,000  &250,000  &250   \\\cline{1-4}
Incubation time  &30 min  &126 steps  &---   \\\cline{1-4}
\end{longtabu}


The pairs of lectins, glycans, and cytokines implemented in the dictionary (vide infra) now (Aug 31, 2018) are\+:

\tabulinesep=1mm
\begin{longtabu} spread 0pt [c]{*{5}{|X[-1]}|}
\hline
\rowcolor{\tableheadbgcolor}\textbf{ Lectin  }&\textbf{ Glycan  }&\textbf{ Glycan type  }&\textbf{ Cytokine  }&\textbf{ Reference   }\\\cline{1-5}
\endfirsthead
\hline
\endfoot
\hline
\rowcolor{\tableheadbgcolor}\textbf{ Lectin  }&\textbf{ Glycan  }&\textbf{ Glycan type  }&\textbf{ Cytokine  }&\textbf{ Reference   }\\\cline{1-5}
\endhead
D\+C-\/\+S\+I\+GN  &Mannan  &Mannose  &I\+L-\/6  &1   \\\cline{1-5}
D\+C-\/\+S\+I\+GN  &Lewis-\/Y  &Fucose  &I\+L-\/27p28  &1   \\\cline{1-5}
Dectin-\/1  &Mannan  &Mannose  &I\+L-\/6  &1   \\\cline{1-5}
\end{longtabu}
1) Geijtenbeek, T. B. H. and Gringhuis, S. I. (2016) C-\/type lectin receptors in the control of T helper cell differentiation. {\itshape Nat Rev Immunol} 16(7)\+:433. 